Revisiting the Classics: Online RL in the Programmable Dataplane

### 2021-06-03 ngni-talk/talk.tex
Pres mode...

	\begin{subequations}
		\begin{gather}
			\delta_t = \overbrace{R_{t+1} + \gamma \acval{S_{t+1}}{A_{t+1}}{\wvec{t}}}^{\mathclap{\substack{\text{New target value:}\\ \text{Reward} + \text{some of the next action's value}}}} - \underbrace{\acval{S_t}{A_t}{\wvec{t}}}_{\mathclap{\text{Current value estimate}}},\\\pause
			\bm{w}_{t+1} = \bm{w}_{t} + \overbrace{\alpha \delta_t}^{\mathclap{\text{Move a little bit of } \delta_t \text{ along...}}} \underbrace{\nabla{\acval{S_t}{A_t}{\wvec{t}}}}_{\mathclap{\text{...the policy's gradient}}},\pause
		\end{gather}%
	\end{subequations}

>>>>

	How should we adjust the value of selected items?
	$$
			\delta_t = \overbrace{R_{t+1} + \gamma \acval{S_{t+1}}{A_{t+1}}{\wvec{t}}}^{\mathclap{\substack{\text{New target value:}\\ \text{Reward} + \text{some of the next action's value}}}} - \underbrace{\acval{S_t}{A_t}{\wvec{t}}}_{\mathclap{\text{Current value estimate}}},
	$$\pause

	Policy parameter update:
	$$
			\bm{w}_{t+1} = \bm{w}_{t} + \overbrace{\alpha \delta_t}^{\mathclap{\text{Move a little bit of } \delta_t \text{ along...}}} \underbrace{\nabla{\acval{S_t}{A_t}{\wvec{t}}}}_{\mathclap{\text{...the policy's gradient}}}.
	$$\pause
